\documentclass[margin=2cm,line]{res}
\usepackage[margin=2cm]{geometry}

\textheight = 10.75 in \topmargin = -.5 in \oddsidemargin -.6in
\evensidemargin -.25in \textwidth=6.15in \itemsep=0in
\parsep=0in

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}
\newenvironment{list3}{
  \begin{list}{}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}
\newenvironment{list4}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

\newcommand{\education}[2]{
{\bf #1}, #2 \\
\vspace*{-.15in}
}

\newcommand{\job}[4]{
{\bf #1} \hfill {\bf #2}\\
{\em #3}: #4
}

\begin{document}

\name{\huge Daniel T. Sank, Ph.D.\vspace*{.1in}}
\address{408 Ellwood Beach Drive \#4 \\ Goleta, CA 93117}
\address{\texttt{sank.daniel@gmail.com}}

\begin{resume}

\section{\sc Education}

\education{University of California, Santa Barbara}{Santa Barbara, California}
\begin{list3}
\item Ph.D. in Physics, September 2014
\item Advisor: John M. Martinis
\item Research group webpage: \texttt{http://www.physics.ucsb.edu/~martinisgroup}
\end{list3}

\education{Yale University}{New Haven, Connecticut}
\begin{list3}
\item B.S. in Physics, May 2007 - with distinction
\item Senior thesis on construction of dual well optical tweezers
\end{list3}

\education{Wootton High School}{Rockville, Maryland}
\begin{list3}
\item Graduated "Best Science Student"
\end{list3}


\section{\sc Professional Experience}

\job
{Google}
{2014-Present}
{Quantum Electronics Engineer}
{Research and development on adiabatic and gate-model quantum computers using superconducting devices.}

\job
{University of California Santa Barbara - Department of Physics}
{2008-2014}
{Graduate Student Researcher}
{Design, test, and fabrication of superconducting electronic devices.
World record superconducting quantum state readout:
99\% accuracy in 120 nanoseconds.}

\job
{Army Research Lab}
{summer 2003}
{Intern}
{Data processing/analysis code for 2D LADAR receiver array.}

\job
{ Goddard Space Flight Center}
{summer 2002}
{Intern}
{Mapping Earth magnetosphere from IG-8 satellite data.}


\section{\sc Skills}

{\bf Microwave Engineering}\\
\vspace*{-.15in}
\begin{list4}
\item Designed and tested 4-channel IQ demodulator (4 GHz - 8 GHz RF band) with digitally controlled IF gain.
Used in Google quantum computing.
\item Arbitrary waveform generation at GHz frequencies using custom FPGA controlled GHz DAC and IQ mixing
\item Phase sensitive microwave pulse demodulation using custom FPGA controlled GHz ADC and IQ mixing
\end{list4}

{\bf Signal Processing and Noise}\\
\vspace*{-.15in}
\begin{list4}
\item Noise measurement/characterization, DC-GHz.
\item Deep knowledge of noise theory and application to real hardware.
\item Produced noise course at Google, a set of technical documents covering the link between Fourier analysis and spectral density, aliasing, spectral leakage, 1-bit ADC signal processing, IQ demodulator noise, and quantum noise.
\end{list4}

{\bf Physics/Math theory and calculation}\\
\vspace*{-.15in}
\begin{list4}
\item I am exceptionally good at applying detailed calculation to real hardware systems.
\end{list4}

\pagebreak

{\bf Programming}\\
\vspace*{-.15in}
\begin{list4}
\item Developer for LabRAD project: open source asynchronous server based lab hardware and data management system. LabRAD is currently used in cutting edge research labs in at least fifteen labs in five countries.\\
(\texttt{https://github.com/martinisgroup/pylabrad})
\item Wrote control software (Python) for custom FPGA controlled two channel GHz ADC board used for phase sensitive microwave pulse demodulation.
\item Creator of \emph{gateCompiler} pulse sequence compiler now in standard use in Google quantum computing effort.
\item Creator and developer of python observer pattern library \\
\quad \texttt{https://github.com/DanielSank/observed}.
\end{list4}

{\bf Microfabrication}\\
\vspace*{-.15in}
\begin{list4}
\item Fabrication of superconducting phase and transmon qubit devices at UCSB Nanofabrication facility
\item Tools: Optical lithography stepper, ICP etch, metal sputter deposition, PECVD
\end{list4}

{\bf Cryogenics}\\
\vspace*{-.15in}
\begin{list4}
\item Dilution and adiabatic demagnetization refrigerators
\end{list4}

\section{\sc Invited talks}
\begin{list3}
\item \textit{Surface spin fluctuations probed with flux noise and coherence in Josephson phase qubits}\\
Zhejiang University of Science and Technology, Hangzhou, Zhejiang Province, China.\\ December 8, 2011
\end{list3}

\section{\sc Teaching}
{\bf University of California, Santa Barbara} \hfill{\bf 2007}
\begin{list4}
\item Analog Electronics
\item Digital Electronics, FPGA programming
\item Quantum Mechanics
\end{list4}
{\bf Yale University} \hfill{\bf 2004-2007}
\begin{list4}
\item Advanced freshman physics, recruited as undergraduate mentor.
\item Conceived of and taught special seminar on linear algebra and Fourier transform methods.
\item Science and Quantitative Reasoning tutoring program staff member.
\end{list4}

{\bf Community}
\begin{list4}
\item Registered panelist on \texttt{reddit.com/r/askscience} as ``DanielSank''
\item Active contributor to \texttt{physics.stackexchange.com} as ``DanielSank''.\\
Highest fraction of accepted answers out of all users.
\end{list4}


\section{\sc Honors and\\ Awards}
\begin{list3}
\item Accepted to Les Houches Summer School on "Quantum Machines" \hfill {\bf 2011}
\item Yale University/Howard Hughes Medical Institute research fellow \hfill {\bf 2005}
\item Yale University Office of the dean summer research fellow \hfill {\bf 2006}
\item Wootton High School named "Best Science Student" \hfill {\bf 2003}
\end{list3}

\section{\sc References}
\begin{list3}
\item Evan Jeffrey (colleague) - \texttt{ejeffrey@gmail.com}
\item Amit Vainsencher (colleague) - \texttt{amit@lazyrabbit.org}
\item Marissa Giustina (colleage) - \texttt{marissa.giustina@gmail.com}
\item John Martinis (manager) - \texttt{jmartinis@google.com}
\item Jason Seifter (friend) - \texttt{seifterj@gmail.com}
\end{list3}

\pagebreak


\section{\sc Publications (refereed)}

\begin{list3}

\item Fast accurate state measurement with superconducting qubits. Evan Jeffrey$^*$, \textbf{Daniel Sank}$^*$, J.Y. Mutus, T.C. White, J. Kelly, R. Barends, Y. Chen, Z. Chen, B. Chiaro, A. Dunsworth, A. Megrant, P.J.J. O'Malley, C. Neill, P. Roushan, A. Vainsencher, J. Wenner, A.N. Cleland, John M. Martinis Phys. Rev. Lett. 112, 190504 (2014). $^*$Equally contributing authors\\

\item Flux noise probed with real time qubit tomography in a Josephson phase qubit. \textbf{Daniel Sank}, M. Lenander, H. Wang, Radoslaw C. Bialczak, Erik Lucero, Matteo Mariantoni, M. Neeley, A.D. O'Connell, M. Weides, J. Wenner, T. White, P. O'Malley, A. Vainsencher, J. Kelly, T. Yamamoto, Y. Yin, J. Zhao, A. N. Cleland, J. M. Martinis. Phys. Rev. Lett. 109, 067001 (2012) \\

\item Thin film dielectric microstrip kinetic inductance detectors. Mazin, B.A., \textbf{Sank, D.}, McHugh, S., Lucero, E.A., Martinis, J., Merrill, A., Gao, J., Pappas, D., Golwala, S., Moore, D., Zmuidzinas, Z. App. Phys. Lett., 96, 102504, (2010) \\

\item Measurement of energy decay in superconducting qubits from nonequilibrium quasiparticles. M. Lenander, H. Wang, Radoslaw C. Bialczak, Erik Lucero, Matteo Mariantoni, M. Neeley, A.D. O'Connell, \textbf{D. Sank}, M. Weides, J. Wenner, T. Yamamoto, Y. Yin, J. Zhao, A. N. Cleland, John M. Martinis. Phys. Rev. B 84, 024501 (2011)

\item Wirebond crosstalk and cavity modes in large chip mounts for superconducting qubits. J. Wenner, M. Neeley, Radoslaw C. Bialczak, M. Lenander, Erik Lucero, A. D. O'Connell, \textbf{D. Sank}, H. Wang, M. Weides, A. N. Cleland, John M Martinis. Supercond. Sci. Technol. 24 (2011) 065001 \\

\item Photon shell game in three-resonator circuit quantum electrodynamics. Matteo Mariantoni, H. Wang, Radoslaw C. Bialczak, M. Lenander, Erik Lucero, M. Neeley, A. D. O'Connell, \textbf{D. Sank}, M. Weides, J. Wenner, T. Yamamoto, Y. Yin, J. Zhao, John M. Martinis, A. N. Cleland. Nature Physics 7, 287-293 (2011) \\

\item Phase qubits fabricated with trilayer junctions. M. Weides, R. C. Bialczak, M. Lenander, E. Lucero, Matteo Mariantoni, M. Neeley, A. D. O'Connell, \textbf{D. Sank}, H. Wang, J. Wenner, T. Yamamoto, Y. Yin, A. N. Cleland, J. Martinis. Superconductor Science and Technology 24, 055005 (2011). \\

\item Fast tunable coupler for superconducting qubits. R. C. Bialczak, M. Ansmann, M. Hofheinz, M. Lenander, E. Lucero, M. Neeley, A. D. O'Connell, \textbf{D. Sank}, H. Wang, M. Weides, J. Wenner, T. Yamamoto, A. N. Cleland, J. M. Martinis. Phys. Rev. Lett. 106, 060501 (2011) \\

\item Deterministic entanglement of photons in two superconducting microwave resonators. H. Wang, Matteo Mariantoni, Radoslaw C. Bialczak, M. Lenander, Erik Lucero, M. Neeley, A. O'Connell, \textbf{D. Sank}, M. Weides, J. Wenner, T. Yamamoto, Y. Yin, J. Zhao, John M. Martinis, A. N. Cleland. PRL 106, 060401 (2011). \\

\item Quantum process tomography of two-qubit controlled-Z and controlled-NOT gates using superconducting phase qubits. T. Yamamoto, M. Neeley, E. Lucero, R. C. Bialczak, J. Kelly, M. Lenander, Matteo Mariantoni, A. D. O'Connell, \textbf{D. Sank}, H. Wang, M. Weides, J. Wenner, Y. Yin, A. N. Cleland, John M. Martinis. PRB 82, 184515 (2010). \\

\item Reduced phase error through optimized control of a superconducting qubit. Erik Lucero, Julian Kelly, Radoslaw C. Bialczak, Mike Lenander, Matteo Mariantoni, Matthew Neeley, A. D. O'Connell, \textbf{Daniel Sank}, H. Wang, Martin Weides, James Wenner, Tsuyoshi Yamamoto, A. N. Cleland, John M. Martinis. PRA 82, 042339 (2010). \\

\item Generation of Three-Qubit Entangled States using Superconducting Phase Qubits. Matthew Neeley, Radoslaw C. Bialczak, M. Lenander, E. Lucero, Matteo Mariantoni, A. D. O'Connell, \textbf{D. Sank}, H. Wang, M. Weides, J. Wenner, Y. Yin, T. Yamamoto, A. N. Cleland, John M. Martinis. Nature 467, 570-573 (2010). \\

\item Quantum Process Tomography of a Universal Entangling Gate Implemented with Josephson Phase Qubits. R. C. Bialczak, M. Ansmann, M. Hofheinz, E. Lucero, M. Neeley, A. D. O'Connell, \textbf{D. Sank}, H. Wang, J. Wenner, M. Steffen, A. N. Cleland, J. M. Martinis. Nature Physics 6, 409-413 (2010). \\

\end{list3}

\pagebreak

\begin{list3}

\item Quantum ground state and single-phonon control of a mechanical resonator. A. D. O'Connell, M. Hofheinz, M. Ansmann, Radoslaw C. Bialczak, M. Lenander, Erik Lucero, M. Neeley, \textbf{D. Sank}, H. Wang, M. Weides, J. Wenner, John M. Martinis, A. N. Cleland. Nature 464, 697-703 (2010). \\

\item Decoherence Dynamics of Complex Photon States in a Superconducting Circuit. H. Wang, M. Hofheinz, M. Ansmann, R. C. Bialczak, Erik Lucero, M. Neeley, A. D. O'Connell, \textbf{D. Sank}, M. Weides, J. Wenner, A. N. Cleland, John M. Martinis. PRL 103, 200404 (2009). \\

\item Improving the Coherence Time of Superconducting Coplanar Resonators. H. Wang, M. Hofheinz, J. Wenner, M. Ansmann, R. C. Bialczak, M. Lenander, E. Lucero, M. Neeley, A. D. O'Connell, \textbf{D. Sank}, M. Weides, A. N. Cleland, John M. Martinis. APL 95, 233508 (2009). \\

\item Violation of Bell's inequality in Josephson phase qubits. Markus Ansmann, H. Wang, Radoslaw C. Bialczak, Max Hofheinz, Erik Lucero, M. Neeley, A. D. O'Connell, \textbf{D. Sank}, M. Weides, J. Wenner, A. N. Cleland, John M. Martinis. Nature 461, 504-506 (2009).

\item Emulation of a Quantum Spin with a Superconducting Phase Qudit. Matthew Neeley, Markus Ansmann, Radoslaw C. Bialczak, Max Hofheinz, Erik Lucero, Aaron D. O'Connell, \textbf{Daniel Sank}, Haohua Wang, James Wenner, Andrew N. Cleland, Michael R. Geller, John M. Martinis. Science 325, 722 (2009). \\

\item Synthesizing arbitrary quantum states in a superconducting resonator. Max Hofheinz, H. Wang, M. Ansmann, Radoslaw C. Bialczak, Erik Lucero, M. Neeley, A. D. O'Connell, \textbf{D. Sank}, J. Wenner, John M. Martinis, A. N. Cleland. Nature 459, 546-549 (2009). \\

\item Measurement of the decay of Fock states in a superconducting quantum circuit. H. Wang, M. Hofheinz, M. Ansmann, R. C. Bialczak, E. Lucero, M. Neeley, A. D. O'Connell, \textbf{D. Sank}, J. Wenner, A. N. Cleland and John M. Martinis. PRL 101, 240401 (2008).
\\
\end{list3}


\end{resume}
\end{document}
