\skill{Microwave Engineering}
{
  {Designed, built, and tested 4-channel IQ demodulator: RF frequency 4 GHz - 8 GHz, IF band dc-400 MHz, with digitally controlled IF gain. Used at Google's quantum computing lab.},
  {Designed and tested superconducting coplanar waveguide filter that improved readout speed of transmon qubits by 100x without sacrificing coherence.}
  % {Arbitrary waveform generation at GHz frequencies using custom FPGA controlled GHz DAC and IQ mixing},
  % {Phase sensitive microwave pulse demodulation using custom FPGA controlled GHz ADC and IQ mixing}
}

\skill{Signal Processing and Noise}
{
  {Noise measurement/characterization, DC-GHz.},
  {Deep knowledge of noise theory and application to real hardware.},
  {Produced noise course at Google, a set of technical documents covering the link between Fourier analysis and spectral density, aliasing, spectral leakage, 1-bit ADC signal processing, IQ demodulator noise, and quantum noise.}
}

%\skill{Physics/Math calculation}
%{I am exceptionally good at applying detailed calculation to real hardware systems.}

\skill{Programming}
{
  {Developer for LabRAD project: open source asynchronous server based lab hardware and data management system. LabRAD is currently used in cutting edge research labs in at least fifteen labs in five countries: \texttt{https://github.com/martinisgroup/pylabrad}},
  {Wrote control software (Python) for custom FPGA controlled two channel GHz ADC board used for phase sensitive microwave pulse demodulation.},
  {Creator of \emph{gateCompiler} pulse sequence compiler now in standard use in Google quantum computing effort.},
  {Creator and developer of python observer pattern library \\ \quad \texttt{https://github.com/DanielSank/observed}.}
}

\newpage

\skill{Microfabrication}
{
  {Fabrication of superconducting phase and transmon qubit devices at UCSB Nanofabrication facility},
  {Tools: Optical lithography stepper, ICP etch, metal sputter deposition, PECVD}
}

\skill{Cryogenics}
{
  {Dilution and adiabatic demagnetization refrigerators}
}
